### 2020-11-10 docs/manuscript.tex
progress on title page

\PaperTitle{
    Predicting HLA associated mutations with a \\ Bayesian regression model
} % Article title

\Authors{} % Authors
% \affiliation{\textsuperscript{1}\textit{Department of Biology, University of Examples, London, United Kingdom}} % Author affiliation
% \affiliation{\textsuperscript{2}\textit{Department of Chemistry, University of Examples, London, United Kingdom}} % Author affiliation
% \affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author

\Keywords{} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

@@

\Abstract{

}

@@

>>>>

\PaperTitle{
    HAMFinder: Combining information to predict HLA-associated mutations with a
    Bayesian regression model
} % Article title

\Authors{Daniel Habermann\textsuperscript{1}, Daniel Hoffmann\textsuperscript{1}} % Authors
\affiliation{\textsuperscript{1}\textit{Department of Biology, University of Duisburg-Essen, Essen, Germany}} % Author affiliation
% \affiliation{\textsuperscript{2}\textit{Department of Chemistry, University of Examples, London, United Kingdom}} % Author affiliation
% \affiliation{*\textbf{Corresponding author}: john@smith.com} % Corresponding author

\Keywords{human leucocyte anigen system, multiple sequence alignment, escape mutations, 
  Bayesian inference, sparsity, horseshoe, epitope prediction} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

@@

\Abstract{
  % - what are HLA associated mutations and why identifying HLA escape is important
  % 
  % - current methods lack important aspects
  % - Progress in Bayesian methods are not reflected in current HLA models
  % - Bayesian statistics provides a coherent framework to combine information from different sources
  % - Using this kind of imformation and new methods improve predicted performance tremendously
  % -
  \\
  \textbf{Motivation} \\
  The human leucoyte antigen system (HLA) is of paramount importance to combat viral
  infections by presenting peptides on the cell surface via MHC I.
  In this way, CD8+ cytotoxic T-Lymphocytes exert a strong selection pressure towards
  virus variants that escape that immune recognition pathway, e.g. through point 
  mutations that decrease binding of the respective peptide to MHC I. \\

  Reliably identifying HLA-associated mutations is important for understanding viral
  evolution, but experimental methods like binding assays are prohibitively expensive
  for large-scale use and fail to recognize other mechanisms of immune escape like
  proteasomal processing.

  One step in finding these mutations is through the statistical analysis
  of sequence data. However, existing methods are based on nullhypothesis significance 
  testing and do not make use of all the available information and therefore have poor
  real-world performance. \\

  \textbf{Results} \\
  Here, we present a Bayesian regression model that is easily extensible to include 
  information from different sources (e.g. epitope prediction software) 
  and makes use of recent advances in Bayesian inference, e.g. by using a sparsifying 
  prior. We show that including this kind of information improves predictive performance 
  considerably over state-of-the-art methods. \\

  \textbf{Availability and Implementation} \\
  The source code of this software is available at 
  \url{http://gogs.uni-due.de/habermann/Escape.git} under a permissive MIT license. \\

  \textbf{Supplementary information} \\
  \url{google.de}[Supplementary data] are available at \textit{Bioinformatics} online. \\
}

@@

\pagebreak

\section{Introduction}
\section{System and methods}
\section{Algorithm}
\section{Implementation}
\section{Discussion}
\section{References}
